### 2013-10-15 inst/doc/README.Rmd
update readme with metadata example

```{r include=FALSE}
opts_chunk$set(tidy=FALSE)
```

@@

```{r eval=FALSE}
library(devtools)
install_github("RNeXML", "ropensci")
library(RNeXML)
```

@@

```{r}
f <- system.file("examples", "trees.xml", package="RNeXML")
tr <- nexml_read(f, "phylo")
plot(tr[[1]])
```

@@

<!---
NOT IMPLEMENTED YET

Extract metadata from the NeXML file:

```{r eval=FALSE} 
ex2 <- nexml_read("treebase1.xml", "nexml")
metadata(ex2)
```

@@

```{r eval=FALSE}
nexml_write(bird.orders, "birds.xml", 
            author="Carl Boettiger <cboettig@ropensci.org>", 
            title = "example NeXML file for bird orders", 
            description = "Example phylogeny taken from the ape documentation showing the major bird orders", 
            in_publication = "doi:10.1010/fakedoi.1234",
            add_itis = TRUE)
```

-->

>>>>

```{r echo=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(tidy=FALSE, warning=FALSE, cache=FALSE)
```

@@

```{r eval=FALSE}
library(devtools)
install_github("RNeXML", "ropensci")
```

@@

```{r}
library(RNeXML)
f <- system.file("examples", "trees.xml", package="RNeXML")
tr <- nexml_read(f, "phylo")
plot(tr[[1]])
```

@@

<!--
Extract metadata from the NeXML file:

```{r eval=FALSE} 
ex2 <- nexml_read(f, "nexml")
metadata(ex2)
```
-->

--------------------------------------------

### Advanced annotation

@@

```{r }
  history <- new("meta", 
      content = "Mapped from the bird.orders data in the ape package using RNeXML",
      datatype = "xsd:string", id = "meta5144", property = "skos:historyNote", 
      'xsi:type' = "LiteralMeta")
  modified <- new("meta",
                  content = "2013-10-04", datatype = "xsd:string", id = "meta5128",
                  property = "prism:modificationDate", 'xsi:type' = "LiteralMeta")
  website <- new("meta", 
                 href = "http://carlboettiger.info", 
                 rel = "foaf:homepage", 'xsi:type' = "ResourceMeta")
  nexml_write(bird.orders, 
              file = "example.xml", 
              additional_metadata = list(history, modified, website), 
              additional_namespaces = c(skos = "http://www.w3.org/2004/02/skos/core#",
                                        prism = "http://prismstandard.org/namespaces/1.2/basic/",
                                        foaf = "http://xmlns.com/foaf/0.1/"))

```

<!--
```{r eval=FALSE}
 nexml_write(bird.orders, "birds.xml", 
            author="Carl Boettiger <cboettig@ropensci.org>", 
            title = "example NeXML file for bird orders", 
            description = "Example phylogeny taken from the ape documentation showing the major bird orders", 
            in_publication = "doi:10.1010/fakedoi.1234",
            add_itis = TRUE)
```
-->
